BHPWAVE: An adiabatic gravitational waveform model for compact objects undergoing quasi-circular inspirals into rotating massive black holes

### 2023-10-25 ms.tex
Updates from Overleaf

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.95\linewidth]{figures/spline_convergence.pdf}
    \caption{Convergence of the maximum fractional interpolation error $\delta_{(n+1,n)}$ as we increase $n$. Increasing $n$ by one amounts to  doubling the sampling density in each dimension of our grid. Thus a power law decay of $2{-4n}$ (dashed blue line) indicates fourth-order convergence of our bicubic spline.}
    \label{fig:fluxSplineConvergence}
\end{figure}

@@

To confirm the numerical accuracy of our interpolated data, we perform a series of comparisons and self-consistency checks. First we assess the accuracy of our flux interpolant by downsampling the data. Let $f^I_{(n,m)}(x,y)$ denote a bicubic spline that interpolates the function $f(x,y)$ using $(2^n+1) \times (2^m+1)$ grid points in $(x,y)$, e.g., $\mathcal{F}_{N(8,7)}^I(\alpha, \chi) = \mathcal{F}_N^I(\alpha, \chi) $. We then estimate the fractional interpolation error for the flux spline $\mathcal{F}_{N(N',M')}^I$ via
\begin{align}
    \delta_{(N',M')}(\alpha, \chi) = \left|1 - \frac{\mathcal{F}_{N(N',M')}^I(\alpha, \chi)}{\mathcal{F}_{N(N'+1,M'+1)}^I(\alpha, \chi)} \right|.
\end{align}
By downsampling the data, we calculate $\delta_{(7,6)}$, $\delta_{(6,5)}$, and $\delta_{(5,4)}$. We plot $\delta_{(7,6)}$ in Figure \ref{fig:fluxSplineError}, demonstrating that $\delta_{(7,6)}<10^{-6}$ across the entire domain. To estimate the interpolation error of our fully-sampled spline, $\delta_{(8,7)}$, we examine the convergence rate of $|| \delta_{(n+1,n)} ||_\infty$ in Figure \ref{fig:fluxSplineConvergence}. We find that $|| \delta_{(n+1,n)} ||_\infty \propto 2^{-4n}$, which is consistent with the standard fourth-order scaling for cubic spline errors ($\delta \sim \Delta x^4$ for grid spacing $\Delta x$). Provided this scaling holds true as we increase the sampling rate, we estimate that $\delta_{(8,7)} \lesssim 5\times 10^{-8}$.

@@

>>>>

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.95\linewidth]{figures/spline_convergence.pdf}
    \caption{Convergence of the maximum fractional interpolation error $||\delta_{(n+1,n)}||_\infty$ as we increase $n$. Increasing $n$ by one amounts to  doubling the sampling density in each dimension of our grid. Thus a power law decay of $2^{-4n}$ (dashed blue line) indicates fourth-order convergence of our bicubic spline.}
    \label{fig:fluxSplineConvergence}
\end{figure}

@@

To confirm the numerical accuracy of our interpolated data, we perform a series of comparisons and self-consistency checks. First we assess the accuracy of our flux interpolant by downsampling the data. Let $f^I_{(n,m)}(x,y)$ denote a bicubic spline that interpolates the function $f(x,y)$ using $(2^n+1) \times (2^m+1)$ grid points in $(x,y)$, e.g., $\mathcal{F}_{N(8,7)}^I(\alpha, \chi) = \mathcal{F}_N^I(\alpha, \chi) $. We then estimate the fractional interpolation error for the flux spline $\mathcal{F}_{N(N',M')}^I$ via
\begin{align}
    \Delta^\mathcal{F}_{(N',M')}(\alpha, \chi) = \left|1 - \frac{\mathcal{F}_{N(N',M')}^I(\alpha, \chi)}{\mathcal{F}_{N(N'+1,M'+1)}^I(\alpha, \chi)} \right|.
\end{align}
By downsampling the data, we calculate $\Delta^\mathcal{F}_{(7,6)}$, $\Delta^\mathcal{F}_{(6,5)}$, and $\Delta^\mathcal{F}_{(5,4)}$. We plot $\Delta^\mathcal{F}_{(7,6)}$ in Figure \ref{fig:fluxSplineError}, demonstrating that $\Delta^\mathcal{F}_{(7,6)}<10^{-6}$ across the entire domain. To estimate the interpolation error of our fully-sampled spline, $\Delta^\mathcal{F}_{(8,7)}$, we examine the convergence rate of $|| \Delta^\mathcal{F}_{(n+1,n)} ||_\infty$ in Figure \ref{fig:fluxSplineConvergence}. We find that $|| \Delta^\mathcal{F}_{(n+1,n)} ||_\infty \propto 2^{-4n}$, which is consistent with the standard fourth-order scaling for cubic spline errors (error $ \sim \Delta x^4$ for grid spacing $\Delta x$). Provided this scaling holds true as we increase the sampling rate, we estimate that $\Delta^\mathcal{F}_{(8,7)} \lesssim 5\times 10^{-8}$.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.95\linewidth]{figures/timeAndPhaseConvergence.pdf}
    \caption{Convergence of the maximum absolute interpolation error for the frequency-weighted time and phase splines, $||\Delta^{\Omega t}_{(n,n)}||_\infty$ (orange squares) and $||\Delta^\Phi_{(n,n)}||_\infty$ (green diamonds), along with the fractional interpolation error for the unweighted time-spline $||\Delta^t_{(n,n)}||_\infty$ (blue diamonds). The dashed lines correspond to a power-law convergence of $2^{4n}$.}
    \label{fig:trajConvergence}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.95\linewidth]{figures/frequencyConvergence.pdf}
    \caption{Convergence of the maximum fractional interpolation error for the frequency spline, $||\Delta^{\Omega}_{(n,n)}||_\infty$.}
    \label{fig:frequencyConvergence}
\end{figure}
